---
title: How to Build a Scatterplot on Rstudio
author: Maddie Castele
date: '2017-09-27'
slug: how-to-build-a-scatterplot-on-rstudio
categories:
  - R
  - Rstudio
tags:
  - scatterplot
---

Scatterplots are a form of Data Visualization. To start building one on Rstudio we have to download these three packages: Lahman, sqldf, and a new package called ggplot2.
```{r}
library(Lahman)
library(sqldf)
library(ggplot2)
```

So, we want to find career strikeouts and career homeruns for all players who have hit 400 or more homeruns total. We are using the command AS to change the column title in the console.This is how we would write this query:
```{r}
query<-"select playerID,sum(HR) as career_HR,sum(SO) as career_SO
from Batting
group by playerID
having sum(HR)>=400"

sqldf(query)
```

Now that we have the data we want to use, let's turn it into a scatterplot. We can also change the size and color of the dots.It's important to keep putting plus signs at the end of each command line so Rstudio knows you are still working on this scatterplot.
```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")
```

To change the main title and axis titles, we add these commands to our code:
```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR),size=3,color="blue")+
  ggtitle("Career Strikeouts VS Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")

```
